Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-21 main.tex
linear

\newcommand{\rectif}[1]{\widehat{#1}}
\newcommand{\graphof}[1]{\llbracket#1\rrbracket}
\newcommand{\compl}[1]{#1^\complement}
%\newcommand{\sublist}[1]{\set{#1}}
%\newcommand{\subst}[2]{#1\mathord{\scriptstyle\mapsto} #2}
\newcommand{\sublist}[1]{[#1]}
\newcommand{\subst}[2]{#1/#2}
\newcommand{\ssubst}[2]{\sublist{\subst{#1}{#2}}}
\newcommand{\substof}[1]{\sigma_{\!#1}}
\newcommand{\rsubstof}[1]{\rho_{\!#1}}
\newcommand{\dsubstof}[1]{\delta_{\!#1}}
\newcommand{\linkingof}[1]{\sim_{#1}}
\newcommand{\mapof}[1]{\lfloor{#1}\rfloor}
\newcommand{\labelof}[1]{\ell(#1)}
\newcommand{\form}[1]{\mathrm{fm}(#1)}
\newcommand{\formtree}[1]{\mathcal{F}(#1)}

@@

\begin{proof}
  That $\graphof A$ is a logical cograph follows immediately from the definition and Theorem~\ref{thm:cograph}.
  The fact that every binder of $\graphof A$ is legal can be proved by
  structural induction on $A$.
  %% :
  %% \begin{itemize}
  %%   \item Trivial if $A$ is an atom.
  %%   \item The induction step uses the following fact:
  %%         if $M$ is a module of $\gG$ and $M' \subseteq M$, then $M'$ is a
  %%         module of $\gG$ if and only if it is a module of $\gG[X]$.
  %% \end{itemize}
  %% \todo{}\lutz{maybe mention also fn 2-5 in Dominic's arxiv-paper}
\end{proof}
%%\juihsuan{I'm still looking for a simple proof}
Note that $\graphof A$ is not necessarily a fograph if $A$ is not
rectified. If $A = (\forall x. p(x)) \vlor (\forall x. q(x))$, then
$\graphof A = \single x \ \single p(x) \ \single x \ \single q(x)$,
the scope of each $x$-binder contains all the vertices, in particular,
the two $x$-binders. On the other hand, there are non-rectified
formulas which are translated to fographs by $\graphof\cdot$. For
example, in $\graphof{(\exists x. p(x)) \vlor (\exists x. q(x))}$,
both $x$-binders are legal, as they are not in each others
scope.\todo{draw the picture}.  For this reason, we call a formula
\bfit{clean} if it does not contain subformulas of the form $(\forall
x.A)\vlor(\forall x.B)$ or $(\exists x.A)\vlan(\exists x.B)$, and no
$x$-quantified formula occurs as subformula of another $x$-quantified
formula. Then we have:

@@

@@

Two atoms are \bfit{pre-dual} if their predicate symbols are dual
(e.g. $p(x, y)$ and $\dual{p}(y, z)$) and two literals are \bfit{pre-dual} if their
labels (atoms) are pre-dual. A \bfit{linked fograph} is a coloured fograph $\gC$ such
that every colour (i.e., equivalence class of~$\linkingof\gC$), called a \bfit{link}, consists of two pre-dual literals, and
every literal is either $\ttt$-labelled or in a link.

Let $\gC$ be a linked fograph. The set of links can be seen as a unification problem
by identifying dual predicate symbols. A \bfit{dualizer} of $\gC$ is a substitution
unifying all the links of $\gC$. Since a first-order unification problem is either
unsolvable or has a most general unifier, we can define the notion of \bfit{most
general dualizer}. A \bfit{dependency} is a pair $\set{\single x, \single y}$ of an
existential binder $\single x$ and a universal binder $\single y$ such that the most
general dualizer assigns to $x$ a term containing $y$. A \bfit{leap} is either a
link or a dependency. The \bfit{leap graph} $\lgC$ of $\gC$ is the undirected
graph $\tuple{\vC, \lpC}$ where $\lpC$ is the set of leaps of $\gC$. A vetex set $W \subseteq \vC$ induces a \bfit{matching} in
$\gC$ if for all $w \in W$, $N(w) \cap W$ is a singleton. We say that $W$ induces a
\bfit{bimatching} in $\gC$ if it induces a matching in $\gC$ and a matching in $\lgC$.

@@

We consider here only the cut-free fragment, as cut-elimination for
deep inference systems has already been discussed
elsewhere~\cite{brunnler:06:herbrand,alertubella:guglielmi:18}.
\juihsuan{references added. Please check if they are the right ones.}
\footnote{In the deep
inference literature, the cut-free fragment is also called the
\emph{down-fragment}. But as we do not discuss the \emph{up-fragment}
here, we omit the down-arrows $\downarrow$ in the rule names.}

@@

\begin{lemma}\label{lem:cw-decomposition}
  For every derivation
  $\vlderivation{
      \vlde{\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{}{B}{
        \vlhy{A}}}$
  there are formulas $A'$ and $B'$ such that 
  \begin{equation*}
    \vlderivation{
      \vlde{\set{\wrD,\fequ}}{}{B}{
        \vlde{\set{\acD}}{}{B'}{
          \vlde{\set{\me,\mfaD,\mexD,\fequ}}{}{A'}{
            \vlhy{A}}}}}
  \end{equation*}
\end{lemma}

@@

@@

\todo{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Translation between $\FOMLS$ and Fonets}

A derivation $\Deri$ is \bfit{rectified} if every line in $\Deri$ is
rectified.  For a non-rectified derivation $\Deri$ in $\FOMLS$ we can
define its \bfit{rectification} $\rectif\Deri$ by recifying each
line. In $\FOMLS$ this can be done inductively, proceeding step-wise
from conclusion to premise, as the only rules involving bound
variables are $\forall$ and $\exists$ which both remove a binder (and
all occurrences of the variable it binds).\footnote{As for formulas,
the rectification of a derivation is unique up to renaming of bound
variables.}\todo{check if we need that $\Deri$ has premise $\ttt$}.

A derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ determines a
substitution which maps the existential bound variables occurring in
$A$ to the terms substituted for them in the instances of the
$\exists$-rule in $\Phi$. We denote this substitution with
$\substof\Phi$. Furthermore, every atom occuring in the conclusion $A$
must be consumed by a unique instance of the rule $\aiD$ in
$\Deri$. This allows us to define a (partial) equivalence relation
$\linkingof\Deri$ on the atom occurrences in $A$ by $a\linkingof\Deri
b$ if $a$ and $b$ are consumed by the same instance of $\aiD$
in~$\Deri$. We call $\linkingof\Deri$ the \bfit{linking} of~$\Deri$.

\begin{lemma}\label{lem:MLS1->fonet}
  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a recified derivation. Then
  the graph $\graphof{A}$ forms a fonet whose linking is
  $\linkingof{\Deri}$ and whose dualizer is
  $\substof{\Deri}$.
\end{lemma}

\begin{thm}
  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be given. Then
  the graph $\graphof{\rectif A}$ forms a fonet whose linking is
  $\linkingof{\rectif\Deri}$ and whose dualizer is
  $\substof{\rectif\Deri}$.
\end{thm}

\begin{proof}
  Apply Lemma~\ref{lem:MLS1->fonet} to the rectification $\rectif\Deri$ of $\Deri$.
\end{proof}

>>>>

\newcommand{\rectif}[1]{\widehat{#1}}

\newcommand{\fographof}[1]{\llbracket#1\rrbracket}
\newcommand{\graphof}[1]{\llbracket#1\rrbracket}
%\newcommand{\graphof}[1]{\mathbb{G}(#1)}

\newcommand{\compl}[1]{#1^\complement}
%\newcommand{\sublist}[1]{\set{#1}}
%\newcommand{\subst}[2]{#1\mathord{\scriptstyle\mapsto} #2}
\newcommand{\sublist}[1]{[#1]}
\newcommand{\subst}[2]{#1/#2}
\newcommand{\ssubst}[2]{\sublist{\subst{#1}{#2}}}
\newcommand{\substof}[1]{\sigma_{\!#1}}
\newcommand{\rsubstof}[1]{\rho_{#1}}
\newcommand{\dsubstof}[1]{\delta_{#1}}
\newcommand{\linkingof}[1]{\sim_{#1}}
\newcommand{\mapof}[1]{\lfloor{#1}\rfloor}
\newcommand{\labelof}[1]{\ell(#1)}
\newcommand{\form}[1]{\mathrm{fm}(#1)}
\newcommand{\formtree}[1]{\mathcal{F}(#1)}

@@

\begin{proof}
  That $\graphof A$ is a logical cograph follows immediately from the definition and Theorem~\ref{thm:cograph}.
  The fact that every binder of $\graphof A$ is legal can be proved by
  structural induction on $A$.
  %% :
  %% \begin{itemize}
  %%   \item Trivial if $A$ is an atom.
  %%   \item The induction step uses the following fact:
  %%         if $M$ is a module of $\gG$ and $M' \subseteq M$, then $M'$ is a
  %%         module of $\gG$ if and only if it is a module of $\gG[X]$.
  %% \end{itemize}
  %% \todo{}\lutz{maybe mention also fn 2-5 in Dominic's arxiv-paper}
\end{proof}
%%\juihsuan{I'm still looking for a simple proof}
Note that $\graphof A$ is not necessarily a fograph if $A$ is not
rectified. If $A = (\forall x. p(x)) \vlor (\forall x. q(x))$, then
$\graphof A = \single x \ \single p(x) \ \single x \ \single q(x)$,
the scope of each $x$-binder contains all the vertices, in particular,
the two $x$-binders. On the other hand, there are non-rectified
formulas which are translated to fographs by $\graphof\cdot$. For
example, in the graph of $(\exists x. p(x)) \vlor (\exists x. q(x))$,
both $x$-binders are legal, as they are not in each others
scope.\todo{draw the picture}.  For this reason, we call a formula
\bfit{clean} if it does not contain subformulas of the form $(\forall
x.A)\vlor(\forall x.B)$ or $(\exists x.A)\vlan(\exists x.B)$, and no
$x$-quantified formula occurs as subformula of another $x$-quantified
formula. Then we have:

@@

Note that even though for every formula $A$ we can obtain an
equivalent clean formula by simply renaming some bound variables, this
is not unique up to $\alpha$-conversion, as it is the case for
rectified formulas.

@@

Two atoms are \bfit{pre-dual} if their predicate symbols are dual
(e.g. $p(x, y)$ and $\dual{p}(y, z)$) and two literals are \bfit{pre-dual} if their
labels (atoms) are pre-dual. A \bfit{linked fograph} $\tuple{\gC,\linkingof\gC}$ is a coloured fograph $\gC$ such
that every colour (i.e., equivalence class of~$\linkingof\gC$), called a \bfit{link}, consists of two pre-dual literals, and
every literal is either $\ttt$-labelled or in a link.

Let $\gC$ be a linked fograph. The set of links can be seen as a unification problem
by identifying dual predicate symbols. A \bfit{dualizer} of $\gC$ is a substitution $\delta$
unifying all the links of~$\gC$. Since a first-order unification problem is either
unsolvable or has a most general unifier, we can define the notion of \bfit{most
general dualizer}. A \bfit{dependency} is a pair $\set{\single x, \single y}$ of an
existential binder $\single x$ and a universal binder $\single y$ such that the most
general dualizer assigns to $x$ a term containing $y$. A \bfit{leap} is either a
link or a dependency. The \bfit{leap graph} $\lgC$ of $\gC$ is the undirected
graph $\tuple{\vC, \lpC}$ where $\lpC$ is the set of leaps of $\gC$. A vetex set $W \subseteq \vC$ induces a \bfit{matching} in
$\gC$ if for all $w \in W$, $N(w) \cap W$ is a singleton. We say that $W$ induces a
\bfit{bimatching} in $\gC$ if it induces a matching in $\gC$ and a matching in $\lgC$.

@@

We consider here only the cut-free fragment, as cut-elimination for
deep inference systems has already been discussed
elsewhere (e.g.~\cite{brunnler:06:herbrand,alertubella:guglielmi:18}).%
%\juihsuan{references added. Please check if they are the right ones.}
\footnote{In the deep
inference literature, the cut-free fragment is also called the
\emph{down-fragment}. But as we do not discuss the \emph{up-fragment}
here, we omit the down-arrows $\downarrow$ in the rule names.}

@@

\begin{lemma}\label{lem:cw-decomposition}
  For every derivation
  $\vlderivation{
      \vlde{\set{\wrD,\acD,\me,\mfaD,\mexD,\fequ}}{}{B}{
        \vlhy{A}}}$
  there are formulas $A'$ and $B'$ such that 
  \begin{equation*}
    \vlderivation{
      \vlde{\set{\wrD,\fequ}}{}{B}{
        \vlde{\set{\acD,\cfaD}}{}{B'}{
          \vlde{\set{\me,\mfaD,\mexD,\fequ}}{}{A'}{
            \vlhy{A}}}}}
  \end{equation*}
\end{lemma}

@@

%%\todo{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{From $\FOMLL$ Proofs to Fonets}

Let $\Pi$ be a $\FOMLL$ proof of a rectified sequent $\sqn\Gamma$. We now show
how $\Pi$ is translated into a linked fograph
$\fographof\Pi=\tuple{\graphof\Gamma,\linkingof\Pi}$. We proceed
inductively, making a case analysis on the last rule in $\Pi$. At the
same time we are constructing a dualizer $\dsubstof\Pi$, so that in the
end we can conclude that $\fographof\Pi$ is in fact a fonet.
\begin{enumerate}
  %\setlength\itemsep{.5ex}
\item $\Pi$ is $\vlinf{\axr}{}{\sqn{a,\cneg a}}{}$ : Then the only
  link is $\set{a, \dual{a}}$, and $\dsubstof\Pi$ is empty.
\item $\Pi$ is $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ : Then
  $\linkingof\Pi$ and $\dsubstof\Pi$ are both empty.
\item The last rule in $\Pi$ is $\vliinf{\mixr}{}{\sqn{\Gamma',\Gamma''}}{\sqn\Gamma'}{\sqn\Gamma''}$ :
  By induction hypothesis, we have proofs $\Pi'$ and $\Pi''$ of $\Gamma'$ and $\Gamma''$, respectively. We have
  $\graphof{\Gamma}=\graphof{\Gamma'}+\graphof{\Gamma''}$ and let
  $$\linkingof\Pi\;=\;\linkingof{\Pi'}\cup\linkingof{\Pi''}
  \qquand
  \dsubstof\Pi=\dsubstof{\Pi'}\cup\dsubstof{\Pi''}$$
\item The last rule in $\Pi$ is $\vlinf{\vlor}{}{\sqn{\Gamma_1,A\vlor
    B}}{\sqn{\Gamma_1,A,B}}$ : By induction hypothesis, there is
  proofs $\Pi'$ of $\Gamma'={\Gamma_1,A,B}$. We have
  $\graphof{\Gamma}=\graphof{\Gamma'}$ and let
  $\linkingof\Pi\;=\;\linkingof{\Pi'}$ and
  $\dsubstof\Pi=\dsubstof{\Pi'}$.
\item The last rule in $\Pi$ is $\vliinf{\vlan}{}{\sqn{\Gamma_1,A\vlan
    B, \Gamma_2}}{\sqn{\Gamma_1,A}}{\sqn{B,\Gamma_2}}$ : By induction
  hypothesis, we have proofs $\Pi'$ and $\Pi''$ of
  $\Gamma'=\Gamma_1,A$ and $\Gamma''=B,\Gamma_2$, respectively. We
  have $\graphof{\Gamma}=\graphof{\Gamma_1}+\mbox{$(\graphof A\times\graphof
  B)$}+\graphof{\Gamma_2}$ and we let
  $$\linkingof\Pi\;=\;\linkingof{\Pi'}\cup\linkingof{\Pi''} \qquand
  \dsubstof\Pi=\dsubstof{\Pi'}\cup\dsubstof{\Pi''}$$
\item The last rule in $\Pi$ is
  $\vlinf{\exists}{}{\sqn{\Gamma_1,\exists x.A}}
  {\sqn{\Gamma_1,A\ssubst{x}{t}}}$ : By induction hypothesis, there is
  a $\Pi'$ of $\Gamma'={\Gamma_1,A\ssubst{x}{t}}$.  For each atom in
  $\Gamma'=\Gamma_1, A \ssubst{x}{t}$, there is a corresponding atom
  in $\Gamma=\Gamma_1, \exists x.A$. We can therefore define the
  linking $\linkingof{\Pi}$ from the linking $\linkingof{\Pi'}$ via
  this correspondence. Then, we let $\dsubstof\Pi$ be
  $\dsubstof{\Pi'}+\ssubst{x}{t}$. Since $\Gamma$ is rectified $x$
  does not yet occur in $\dsubstof{\Pi'}$. Hence $\dsubstof\Pi$ is a
  dualizer of $\fographof\Pi$.
\item The last rule in $\Pi$ is $\vlinf{\forall}{\text{($x$ not free
    in $\Gamma_1$)}}{\sqn{\Gamma_1,\forall x.A}}{\sqn{\Gamma_1,A}}$ :
  By induction hypothesis, there is a proof $\Pi'$ of
  $\Gamma'={\Gamma_1,A}$, which has the same atoms as in
  $\Gamma=\Gamma_1, \forall x.A$.  Hence, we can let
  $\linkingof\Pi\;=\;\linkingof{\Pi'}$ and
  $\dsubstof\Pi=\dsubstof{\Pi'}$. 
\end{enumerate}
%\end{itemize}

\begin{thm}
  \label{thm:MLL1->fonet}
  If $\Pi$ is a $\FOMLL$ proof of a rectified sequent $\sqn\Gamma$,
  then $\fographof\Pi$ is a fonet and $\dsubstof\Pi$ is a dualizer for it.
\end{thm}

\begin{proof}
  We have to show that none of the operations above can introduce a
  bimatching. For cases 1--6, this is immediate. For case 7, observe
  that there is a potential dependency from each existential binder in
  $\graphof{\Gamma'}$ to the new $x$-binder $\single x$ in
  $\graphof{\Gamma}$. However, observe that this $\single x$ vertex is
  not connected to any vertex in $\graphof{\Gamma'}$, and hence no
  such new dependency can be extended to a bimatching. That
  $\dsubstof\Pi$ is a dualizer for $\fographof\Pi$ follows immediately
  from the construction. Hence,  $\fographof\Pi$ is a fonet.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{From $\FOMLS$ Proofs to Fonets}

There is a more direct path from a $\FOMLL$ proof $\Pi$ of a rectified
sequent $\Gamma$ to the linked fograph $\fographof\Pi$: simply take
the fograph $\graphof\Gamma$, and let the equivalence classes of
$\linkingof\Pi$ be all the atom pairs that meet in an instance of
$\ax$, and $\dsubstof\Pi$ is simply the collection of all subtitutions
of all the instances of the $\exists$-rule in $\Pi$.
%
We have chosen the more cumbersome path above because it gives us a
direct proof of Theorem~\ref{thm:MLL1->fonet}.
%
However, for translating $\FOMLS$ derivation into fonets, we employ
exactly that direct path.

A derivation $\Deri$ in $\FOMLS$ is \bfit{rectified} if every line in $\Deri$ is
rectified.

\begin{lemma}
  Let  $\Deri$ be a $\FOMLS$ proof of a formula $A$. Then $\Deri$ is rectified iff $A$ is rectified.
\end{lemma}

\begin{proof}
   The only rules involving bound
   variables are $\forall$ and $\exists$ which both remove a binder (and
   all occurrences of the variable it binds).
\end{proof}

Hence, for a non-rectified  $\FOMLS$ derivation $\Deri$ in $\FOMLS$ we can
define its \bfit{rectification} $\rectif\Deri$ inductively, by recifying each
line, proceeding step-wise
from conclusion to premise.\footnote{As for formulas,
the rectification of a derivation is unique up to renaming of bound
variables.}

A rectified derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ determines a
substitution which maps the existential bound variables occurring in
$A$ to the terms substituted for them in the instances of the
$\exists$-rule in $\Phi$. We denote this substitution with
$\dsubstof\Phi$ and call it the \bfit{dualizer} of $\Deri$. Furthermore, every atom occuring in the conclusion $A$
must be consumed by a unique instance of the rule $\aiD$ in
$\Deri$. This allows us to define a (partial) equivalence relation
$\linkingof\Deri$ on the atom occurrences in $A$ by $a\linkingof\Deri
b$ if $a$ and $b$ are consumed by the same instance of $\aiD$
in~$\Deri$. We call $\linkingof\Deri$ the \bfit{linking} of~$\Deri$.

\begin{thm}\label{thm:MLS1->fonet}
  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a recified derivation. Then
  $\tuple{\graphof{A},\linkingof{\Deri}}$ is fonet and $\dsubstof{\Deri}$ is a dualizer for it.
\end{thm}

\begin{proof}
  We have to show that no inference rule in $\FOMLS$ can introduce a
  bimatching. For the rules $\forall$, $\aiD$, $\tttD$, $\fequ$, and
  $\mix$, this is immediate, as they do not introduce new edges in the
  cograph connecting two vertices that are each incident to a leap
  edge. The only rules that can do that are $\sw$ and $\exists$. For the $\sw$-rule, we refer reader to~\cite{retore:???} or \cite{gug:SIS} or \cite{dissvonlutz} where this property has been shown in detail. For the rule $\exists$, a potential bimatching can only be created by a dependency between the \todo{need frame?} 
\end{proof}

\begin{remark}
  There is an alternative path of proving Theorem~\ref{thm:MLS1->fonet}
  by translating $\Deri$ to an $\FOMLL$-proof $\Pi$, observing that
  this process preserves the linking and the dualizer. However, for
  this, we have to extent the construction above to the $\cut$-rule,
  and then show that linking and dualizer of a sequent proof $\Pi$ are
  invariant under cut elimation. This can be done similarly to
  unification nets in~\cite{hughes:unifn}.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{From Fonets to $\FOMLL$ Proofs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{From Fonets to $\FOMLS$ Proofs}

%% \begin{thm}
%%   Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be given. Then
%%   the graph $\graphof{\rectif A}$ forms a fonet whose linking is
%%   $\linkingof{\rectif\Deri}$ and whose dualizer is
%%   $\substof{\rectif\Deri}$.
%% \end{thm}

%% \begin{proof}
%%   Apply Lemma~\ref{lem:MLS1->fonet} to the rectification $\rectif\Deri$ of $\Deri$.
%% \end{proof}

@@

\todo{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
